
# This script borrows heavily from a similar script from MB1

```{r chunk-opts, echo=FALSE}
opts_chunk$set(echo = FALSE)
```

```{r read_data}
d <- read_csv(here("processed_data","02_validated_output.csv"))
source(here("helper/preprocessing_helper.R"))
```

```{r lab_stats}
# Cache lab stats pre-exclusion for lab-based exclusions. 

lab_contribs_pre_exclusion <- d %>%
  group_by(lab) %>%
  summarise(n = length(unique(subid)))
```

```{r pilot}
# We exclude kids who are explicitly marked as pilot.
d <- exclude_by(d, quo(pilot), quiet = TRUE)
```

```{r lab }
# Exclude labs from bll-umanitbo, after discussion with lab that they could not reliably code their data

d <- d %>%
  filter(lab != "bll-umanitoba")


```
* *Lab reliability*. Data from one laboratory were excluded as the lab could not achieve an acceptable level of inter-rater reliability, due to difficulty coding infant eye movements from the available videos.



```{r age}
# We exclude kids who are outside of the 6-9 or 12-15 month age range. 
d <- d %>%
  mutate(out_of_age = case_when(
    age_mo < 6 ~ TRUE,
    age_mo > 15 ~ TRUE,
    age_mo > 9 & age_mo < 12 ~ TRUE,
    TRUE ~ FALSE
  ))

out_of_age <- exclude_by(d, quo(out_of_age),
                   return_pcts = TRUE, 
                   quiet = TRUE)

d <- out_of_age$data
```

* *Age*. There were `r out_of_age$percents$any_sum` (`r round(out_of_age$percents$any_mean*100, 1)`%) infants who were tested but were out of our target age groups (6-9 months and 12-15 months).

```{r}

lang_incl <- exclude_by(d, quo(lang_incl), action = "include", 
                   return_pcts = TRUE, 
                   quiet = TRUE)
d <- lang_incl$data
```

* *Language background*. There were `r lang_incl$percents$any_sum` (`r round(lang_incl$percents$any_mean*100, 1)`%) infants who were tested but did not meet our inclusion criteria for either the monolingual or bilingual group.  For example, an infant who heard English 20% of the time and Italian 80% of the time woudl not meet the criteria as either monolingual (at least 90% exposure to one language) or bilingual (at least 25% exposure to each of two languages).


```{r}
full_term <- exclude_by(d, quo(full_term), action = "include", 
                return_pcts = TRUE, 
                quiet = TRUE)

d <- full_term$data
```

* *Full-term*. We defined full term as gestation times greater than or equal to 37 weeks. `r full_term$percents$any_sum` (`r round(full_term$percents$any_mean*100, 1)`%) infants were tested but did not meet this criterion.

```{r}
ndd <- exclude_by(d, quo(td), action = "include", 
                return_pcts = TRUE, 
                quiet = TRUE)

d <- ndd$data
```

* *No diagnosed developmental disorders*. We excluded data from `r ndd$percents$any_sum` (`r round(ndd$percents$any_mean*100, 1)`%) infants with with parent-reported developmental disorders or sensory impairments.

```{r trial_errors}
trial_err <- exclude_by(d, quo(trial_error), 
                  setting = "any", 
                  return_pcts = TRUE, 
                  quiet = TRUE)

d <- trial_err$data
```


```{r}
#store an additional dataframe containing information on session error types
session_error_type <- d %>%
  filter(session_error) %>%
  distinct(lab, subid,session_error_type) %>%
  count(session_error_type)
 # distinct(lab, subid,session_error_type_recoded) %>%
#  count(session_error_type_recoded)

sessionerr <- exclude_by(d, quo(session_error), 
                         action = "exclude", 
                         return_pcts = TRUE, 
                         quiet = TRUE)

d <- sessionerr$data
```

There were  `r sessionerr$percents$any_sum` (`r round(sessionerr$percents$any_mean*100, 2)`%) infants excluded from the analysis due to issues such including equipment (`r session_error_type$n[session_error_type$session_error_type_recoded=="equipment failure"]` experimenter error, `r session_error_type$n[session_error_type$session_error_type_recoded=="experimenter error"]` infants for or parental/outside interference `r session_error_type$n[session_error_type$session_error_type_recoded=="outside interference"]`.



