
# This script borrows heavily from a similar script from MB1

```{r chunk-opts, echo=FALSE}
opts_chunk$set(echo = FALSE)
```

```{r read_data}
d <- read_csv(here("processed_data","02_validated_output.csv"))
source(here("helper/preprocessing_helper.R"))
```

```{r lab_stats}
# Cache lab stats pre-exclusion for lab-based exclusions. 

lab_contribs_pre_exclusion <- d %>%
  group_by(age_group, lab) %>%
  summarise(n = length(unique(subid)))
```

```{r pilot}
# We exclude kids who are explicitly marked as pilot.
d <- exclude_by(d, quo(pilot), quiet = TRUE)
```


Labs were asked to submit all data collected as part of the study to the analysis team. Data were first screened to determine whether labs contributed useable data, and whether infants met our inclusion criteria. Note that some infants had more than one reason for exclusion, and exclusion criteria were applied sequentially.

```{r lab }
# Exclude labs from bll-umanitoba, after discussion with lab that they could not reliably code their data
# For now, exclude

d <- d %>%
  mutate(lab_excluded = case_when(
    lab == "bll-umanitoba" ~ TRUE,
    lab == "babylab-westernsydney" ~ TRUE,
    TRUE ~ FALSE
  ))


lab_excluded <- exclude_by(d, quo(lab_excluded),
                   return_pcts = TRUE, 
                   quiet = TRUE)

d <- lab_excluded$data


```

* *Lab reliability*. Data from two of the labs using the handcoding method were excluded after extensive discussions with the participating labroatories. One lab could not achieve an acceptable level of inter-rater reliability, due to difficulty coding infant eye movements from the available videos. A second lab initially coded the data incorrectly (i.e., coded face-to-object saccades differently than had been specififed), but then insufficient resources to re-code the data. There were `r lab_excluded$percents$any_sum` (`r round(lab_excluded$percents$any_mean*100, 1)`%) infants who were tested in these labs.

```{r age}
# We exclude kids who are outside of the 6-9 or 12-15 month age range. 
d <- d %>%
  mutate(out_of_age = case_when(
    age_mo < 6 ~ TRUE,
    age_mo > 15 ~ TRUE,
    age_mo > 9 & age_mo < 12 ~ TRUE,
    TRUE ~ FALSE
  ))

out_of_age <- exclude_by(d, quo(out_of_age),
                   return_pcts = TRUE, 
                   quiet = TRUE)

d <- out_of_age$data
```

* *Age*. There were `r out_of_age$percents$any_sum` (`r round(out_of_age$percents$any_mean*100, 1)`%) infants who were tested but were out of our target age groups (6-9 months and 12-15 months).

```{r}

lang_incl <- exclude_by(d, quo(lang_incl), action = "include", 
                   return_pcts = TRUE, 
                   quiet = TRUE)
d <- lang_incl$data
```

* *Language background*. There were `r lang_incl$percents$any_sum` (`r round(lang_incl$percents$any_mean*100, 1)`%) infants who were tested but did not meet our inclusion criteria for either the monolingual or bilingual group.  For example, an infant who heard English 20% of the time and Italian 80% of the time woudl not meet the criteria as either monolingual (at least 90% exposure to one language) or bilingual (at least 25% exposure to each of two languages).


```{r}
full_term <- exclude_by(d, quo(full_term), action = "include", 
                return_pcts = TRUE, 
                quiet = TRUE)

d <- full_term$data
```

* *Full-term*. We defined full term as gestation times greater than or equal to 37 weeks. There were `r full_term$percents$any_sum` (`r round(full_term$percents$any_mean*100, 1)`%) infants who were tested but did not meet this criterion.

```{r}
ndd <- exclude_by(d, quo(td), action = "include", 
                return_pcts = TRUE, 
                quiet = TRUE)

d <- ndd$data
```

* *No diagnosed developmental disorders*. We excluded data from `r ndd$percents$any_sum` (`r round(ndd$percents$any_mean*100, 1)`%) infants with with parent-reported developmental disorders or sensory impairments.

```{r trial_errors}
trial_err <- exclude_by(d, quo(trial_error), 
                  setting = "any", 
                  return_pcts = TRUE, 
                  quiet = TRUE)

d <- trial_err$data
```


```{r}
#store an additional dataframe containing information on session error types
session_error_type <- d %>%
  filter(session_error) %>%
#  distinct(lab, subid, session_error_type) %>%
 # count(session_error_type)
  distinct(lab, subid,session_error_type_recoded) %>%
  count(session_error_type_recoded)

sessionerr <- exclude_by(d, quo(session_error),
                         action = "exclude",
                         return_pcts = TRUE,
                         quiet = TRUE)

d <- sessionerr$data
```

* *Session errors* There were `r sessionerr$percents$any_sum` (`r round(sessionerr$percents$any_mean*100, 2)`%) infants excluded from the analysis due to issues including: (`r session_error_type$n[session_error_type$session_error_type_recoded=="equipment failure"]` for equipment failure,  experimenter error, `r session_error_type$n[session_error_type$session_error_type_recoded=="experimenter error"]` for experimenter error, `r session_error_type$n[session_error_type$session_error_type_recoded=="fussy"]` for fussiness, and `r session_error_type$n[session_error_type$session_error_type_recoded=="outside interference"]` for parental/outside interference.

```{r}
n_shifts <- exclude_by(d, quo(shifts_incl), action = "include", 
                return_pcts = TRUE, 
                quiet = TRUE)

d <- n_shifts$data
```

* *Insufficient face-to-object saccades* Following Senju and Csibra (2008), and per our pre-registration, we also excluded any infant who did not make at least one face-to-object saccade during the window of analysis in at least three of the six trials.  A further `r n_shifts$percents$any_sum` (`r round(n_shifts$percents$any_mean*100, 2)`%) infants were excluded from analyses for this reason.
