```{r chunk-opts, echo=FALSE}
opts_chunk$set(echo = FALSE)
```

```{r read_data}
d <- read_csv(here("processed_data","02_validated_output.csv"))
source(here("helper/preprocessing_helper.R"))
```

```{r lab_stats}
# Cache lab stats pre-exclusion for lab-based exclusions. 

lab_contribs_pre_exclusion <- d %>%
  group_by(age_group, lab) %>%
  summarise(n = length(unique(subid)))
```

```{r pilot}
# We exclude kids who are explicitly marked as pilot.
d <- exclude_by(d, quo(pilot), quiet = TRUE)
```


Labs were asked to submit all data collected as part of the study to the analysis team. Data were first screened to determine whether labs contributed useable data and whether infants met our inclusion criteria. Note that some infants had more than one reason for exclusion, and exclusion criteria were applied sequentially.

```{r lab }
# Exclude labs from bll-umanitoba, after discussion with lab that they could not reliably code their data
# For now, exclude

d <- d %>%
  mutate(lab_excluded = case_when(
    lab == "bll-umanitoba" ~ TRUE,
    lab == "babylab-westernsydney" ~ TRUE,
    TRUE ~ FALSE
  ))


lab_excluded <- exclude_by(d, quo(lab_excluded),
                   return_pcts = TRUE, 
                   quiet = TRUE)

d <- lab_excluded$data


```

* *Lab reliability*. Data from two of the labs using the hand-coding method were excluded after extensive discussions with the participating laboratories. One lab could not achieve an acceptable level of inter-rater reliability, due to difficulty coding infant eye movements from the available videos. A second lab initially coded the data incorrectly (i.e., coded gaze shift from face to object differently than had been specified), but then had insufficient resources to re-code the data. There were `r lab_excluded$percents$any_sum` (`r round(lab_excluded$percents$any_mean*100, 1)`%) infants who were tested in these labs.

```{r age}
# We exclude kids who are outside of the 6-9 or 12-15 month age range. 
d <- d %>%
  mutate(out_of_age = case_when(
    age_mo < 6 ~ TRUE,
    age_mo > 15 ~ TRUE,
    age_mo > 9 & age_mo < 12 ~ TRUE,
    TRUE ~ FALSE
  ))

out_of_age <- exclude_by(d, quo(out_of_age),
                   return_pcts = TRUE, 
                   quiet = TRUE)

d <- out_of_age$data
```

* *Age*. There were `r out_of_age$percents$any_sum` (`r round(out_of_age$percents$any_mean*100, 1)`%) infants who were tested but were out of our target age groups (6-9 months and 12-15 months).

```{r}

lang_incl <- exclude_by(d, quo(lang_incl), action = "include", 
                   return_pcts = TRUE, 
                   quiet = TRUE)
d <- lang_incl$data
```

* *Language background*. There were `r lang_incl$percents$any_sum` (`r round(lang_incl$percents$any_mean*100, 1)`%) infants who were tested but did not meet our inclusion criteria for either the monolingual or bilingual group.  For example, an infant who heard English 20% of the time and Italian 80% of the time would not meet the criteria as either monolingual (at least 90% exposure to one language) or bilingual (at least 25% exposure to each of two languages).


```{r}
full_term <- exclude_by(d, quo(full_term), action = "include", 
                return_pcts = TRUE, 
                quiet = TRUE)

d <- full_term$data
```

* *Full-term*. We defined full-term as gestation times greater than or equal to 37 weeks. There were `r full_term$percents$any_sum` (`r round(full_term$percents$any_mean*100, 1)`%) infants who were tested but did not meet this criterion.

```{r}
ndd <- exclude_by(d, quo(td), action = "include", 
                return_pcts = TRUE, 
                quiet = TRUE)

d <- ndd$data
```

* *No diagnosed developmental disorders*. We excluded data from `r ndd$percents$any_sum` (`r round(ndd$percents$any_mean*100, 1)`%) infant with a parent-reported developmental disorder.

```{r trial_errors}
trial_err <- exclude_by(d, quo(trial_error), 
                  setting = "any", 
                  return_pcts = TRUE, 
                  quiet = TRUE)

d <- trial_err$data
```


```{r}
#store an additional dataframe containing information on session error types
session_error_type <- d %>%
  filter(session_error) %>%
#  distinct(lab, subid, session_error_type) %>%
 # count(session_error_type)
  distinct(lab, subid,session_error_type_recoded) %>%
  count(session_error_type_recoded)

sessionerr <- exclude_by(d, quo(session_error),
                         action = "exclude",
                         return_pcts = TRUE,
                         quiet = TRUE)

d <- sessionerr$data
```

* *Session errors*. There were `r sessionerr$percents$any_sum` (`r round(sessionerr$percents$any_mean*100, 2)`%) infants excluded from the analysis due to issues including: `r session_error_type$n[session_error_type$session_error_type_recoded=="equipment failure"]` for equipment failure, `r session_error_type$n[session_error_type$session_error_type_recoded=="fussiness"]` for fussiness, and `r session_error_type$n[session_error_type$session_error_type_recoded=="outside interference"]` for parental/external interference.

```{r}
n_shifts <- exclude_by(d, quo(shifts_incl), action = "include", 
                return_pcts = TRUE, 
                quiet = TRUE)

d <- n_shifts$data

#Duplicating the data set for comparison in the next chunk
d_after_previousscreening <- d

```

* *Insufficient face-to-object saccades*. Following Senju and Csibra (2008), and per our pre-registration, we also excluded any infant who did not make at least one gaze shift from face to object during the window of analysis in at least three of the six trials.  A further `r n_shifts$percents$any_sum` (`r round(n_shifts$percents$any_mean*100, 2)`%) infants were excluded from analyses for this reason. 


```{r}

# We exclude trials where no look towards the congruent or incongruent object was made.

d <- d %>%
  replace_na(list("n_shift_congruent" = 0, "n_shift_incongruent" = 0)) %>%
  mutate(look_excluded = case_when(
    !(n_shift_congruent + n_shift_incongruent) > 0 ~ TRUE,
    TRUE ~ FALSE
  ))
  
n_nolook <- d %>%
  count(look_excluded, name = "n") 

d <- d %>%
  filter(look_excluded == "FALSE")

# The total number of valid trials left after all the screening procedures
valid_trial <- d %>%
  count(age_group, lang_group, name = "valid_trial") %>%
  add_row(age_group = "total", lang_group = "trial", valid_trial = sum(.$valid_trial)) %>%
  unite(group, c(age_group, lang_group), sep = " ", remove = TRUE)

#Comapre to the data that were left after the previous screenings
d_compare <- d_after_previousscreening %>%
  count(age_group, lang_group, name = "trials_left") %>%
  add_row(age_group = "total", lang_group = "trial", trials_left = sum(.$trials_left)) %>%
  unite(group, c(age_group, lang_group), sep = " ", remove = TRUE) %>%
  left_join(., valid_trial) %>%
  mutate(percentage = (valid_trial/trials_left)*100)

```

* *Failure to attend*. We also excluded any trials in which infants did not look at the congruent or incongruent object during the window of analysis. This meant that each infant contributed a different number of trials. An additional `r n_nolook$n[n_nolook$look_excluded =="TRUE"]` trials (`r round(((n_nolook$n[n_nolook$look_excluded =="TRUE"]) / nrow(d)) *100, 2)`%) were excluded from the analyses. This left us with a total number of `r d_compare$valid_trial[d_compare$group == "total trial"]` valid trials (`r round(d_compare$percentage[d_compare$group == "total trial"], 2)`% of the data after the previous screenings) for later analyses: `r d_compare$valid_trial[d_compare$group == "6-9 mo monolingual"]` trials for 6-to-9-month-old monolinguals (`r round(d_compare$percentage[d_compare$group == "6-9 mo monolingual"], 2)`% of the data), `r d_compare$valid_trial[d_compare$group == "12-15 mo monolingual"]` trials for 12-to-15-month-old monolinguals (`r round(d_compare$percentage[d_compare$group == "12-15 mo monolingual"], 2)`% of the data), `r d_compare$valid_trial[d_compare$group == "6-9 mo bilingual"]` trials for 6-to-9-month-old bilinguals (`r round(d_compare$percentage[d_compare$group == "6-9 mo bilingual"], 2)`% of the data), and `r d_compare$valid_trial[d_compare$group == "12-15 mo bilingual"]` trials for 12-to-15-month-old bilinguals (`r round(d_compare$percentage[d_compare$group == "12-15 mo bilingual"], 2)`% of the data).